---
bibliography:  guidance.bib
#csl: apsr.csl
biblio-style: apsr
output: html_document
---

```{r, include=FALSE}
source(here::here("setup.R"))
```


```{r guidance}
d <- readxl::read_excel(here("bib/Guidance Output.xlsx"), range = "Main Results!A6:S56")

d %<>% gather(key = "model", value = "value", -group, -term, -number)

d$value %<>% as.numeric()

d %<>% filter(!is.na(value), !is.na(number))

d %<>% spread(key = number, value = value)

d %<>% 
  mutate(model = str_remove(model, "..[0-9].*")) %>% 
  rename(std.error = se) 

d %<>% rename(type = group)


# install.packages("dotwhisker")
library(dotwhisker)
  
guidplot <- function(d){  
    dwplot(d, 
           dodge_size = 0.8,
           vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2), # plot line at zero _behind_ coefs
       dot_args = list(aes(shape = model)) ) +
    scale_color_viridis_d(option = "B", begin = 0, end = .8) +
    labs(color = "Model", shape = "Model",
         x = "Estimate",
         title = "Perceived Influence and Lobbying Success
(Observational Data)")
         #caption = 
#"Intervals for p<=.05 with two-tailed tests and 
#robust standard errors clustered by rule")
}
```

# Options 1 and 2, presenting all results:

## Two options for core models:
```{r guidance-figure1, fig.height=3.5}
p <- d %>% 
  filter(str_detect(model, "1|2|5|6")) %>% 
  guidplot() 

b <- list(c("Rule Characteristics", "Comments" , "Salience") 
          )
p%>%
  add_brackets(b)

p+ facet_grid(type ~., scales = "free_y", drop = TRUE) 

```

## Two options for expanded models:
```{r guidance-figure2, fig.height=7.5}

p <- d %>% 
  filter(str_detect(model, "3|4|7|8")) %>% 
  guidplot()


b <- list(c("Org. Characteristics", "Health or Health Care" , "Size"),
          c("Rule Characteristics", "Comments" , "Salience") 
          )

p %>%
  add_brackets(b)

p+ facet_grid(type ~., scales = "free_y", drop = TRUE) 
```

# Option 3, presenting only the Guidance coeficients

```{r guidance-figure3}
d %>% 
  filter(term == "Guidance Document") %>% 
  dwplot(dodge_size = 0.8,
           vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2) ) +
    scale_color_viridis_d(option = "B", begin = 0, end = .8) +
    labs(color = "Model", shape = "Model",
         x = "Estimate",
         title = "Perceived Influence and Lobbying Success
(Observational Data)")

```

# Citations

@Anthony1992

@Baumgartner2009

@Baumgartner1993

@Baumgartner2001

@Bentham1843

@Browne1990

@Carpenter2002

@Carpenter2014a

@Coglianese2009

@Davis1971

@Dur2007

@Epstein1995

@FoodandDrugAdministration2011

@Franklin2010

@Funk2001

@Furlong1998

@Furlong2005

@Garrett2006

@Gluck2015

@Golden1998

@Graham2015

@Greve2014

@Haeder2015

@Hojnacki2012

@Hickman2009

@Hrebenar1996

@Hwang2014

@Kaufman1981

@Kaufman2001

@Kerwin2018

@Kingdon1995

@Kluver2013

@Levin2018

@Lewis2011

@Magill2004

@Mahoney2007JPP

@Manning1996

@Mantel2009

<!--@Mashaw1997-->

@McCubbins1987

@McCubbins1987

@Mendelson2007

@Naughton2009

@OfficeofManagementandBudget2007

@Parrillo2019

@Romano2014

@Romano2018

@Raso2010

@Rourke1984

@Rosenbloom2000

@Sabatier1988

@Schattschneider1975

@Seidenfeld2011

@Shapiro2014

@Stack2016

@Truman1951

@Warren2011

@West1995

@West2004

@Yackee2019

@Yackee2006JOP

@Young2017

# Bibliography