---
bibliography:  guidance.bib
#csl: apsr.csl
biblio-style: apsr
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r, include=FALSE}
source(here::here("setup.R"))
```


```{r guidance}
d <- readxl::read_excel(here("bib/Guidance Output.xlsx"), range = "Main Results!A6:S56")

d %<>% gather(key = "model", value = "value", -group, -term, -number)

d$value %<>% as.numeric()

d %<>% filter(!is.na(value), !is.na(number))

d %<>% spread(key = number, value = value)

d %<>% 
  mutate(model = str_remove(model, "..[0-9].*")) %>% 
  rename(std.error = se) 

d %<>% rename(type = group)

d %<>% filter(str_detect(model, "[1-4]"))

# Order models 
d$model <- factor(d$model, 
levels = unique(d$model), 
labels = unique(d$model))



# set up colors
library(viridisLite)

# 6 models paired shapes 
shapes <- c(15,0,16,1)
names(shapes) <- levels(d$model)
colors <- viridis(length(levels(d$model)), option = "B", begin = 0, end = .8)
names(colors) <- names(shapes)

# install.packages("dotwhisker")
library(dotwhisker)
data <- "Perceived Influence and Lobbying Success\n(Observational Data)"
guidplot <- function(d, data){  
    dwplot(d %>% arrange(desc(model)), 
           dodge_size = 0.8,
           vline = geom_vline(xintercept = 0, 
                              colour = "grey60", 
                              linetype = 2), # plot line at zero _behind_ coefs
           dot_args = list(aes(shape = (model)) ) ) +
    labs(color = "Model", shape = "Model",
         x = "Estimate",
         title = data)+
         # caption = "Intervals for p<=.05,\ntwo-tailed tests,\nrobust standard errors clustered by rule")  +
    #guides(colour = guide_legend(reverse=T),shape = guide_legend(reverse=T)) +
    #ggplot2::annotate(ymin = seq(.5,length(unique(d$term)), 2), ymax = seq(1.5,length(unique(d$term))+1, 2), 
    #         xmin = -Inf, xmax = Inf, 
    #         geom = "rect", alpha = 0.1) +
    scale_shape_manual(values=shapes, breaks = levels(d$model)) +
    scale_color_manual(values=colors, breaks = levels(d$model)) + 
    theme(panel.grid.major.y = element_blank())
}
```

# Observational results:

## Core models:
```{r guidance-figure1, fig.height=3.5}
p <- d %>% 
  filter(str_detect(model, "1|3")) %>% 
  guidplot(data) 

b <- list(c("Rule Characteristics", "Comments" , "Salience") )
p%>%
  add_brackets(b)

# p+ facet_grid(type ~., scales = "free_y", drop = TRUE) 

```

## Expanded models:
```{r guidance-figure2, fig.height=7.5}

p <- d %>% 
  filter(str_detect(model, "1|2|3|4")) %>% 
  guidplot(data)


b <- list(c("Org. Characteristics", "Health or Health Care" , "Size"),
          c("Rule Characteristics", "Comments" , "Salience") 
          )

p %>%
  add_brackets(b)

# p+ facet_grid(type ~., scales = "free_y", drop = TRUE) 
```

## Only the Guidance coeficients

```{r guidance-figure3}
data <- "Perceived Influence and Lobbying Success
(Observational Data)"
d %>% 
  filter(str_detect(model, "1|2|3|4")) %>% 
  filter(term == "Guidance Document") %>% 
  guidplot(data)
```


# Experiment Results (dummy)
```{r guidance-exp, fig.height=2.5}
data <- "Estimates of Hypothetical Influence
(Experimental Data)"
d <- readxl::read_excel(here("bib/Guidance Output.xlsx"), range = "Experiment!A6:O41")

d %<>% fill(term) %>% fill(type)

d %<>% gather(key = "model", value = "value", -type, -term, -number)

d$value %<>% as.numeric()

d %<>% filter(!is.na(value), !is.na(number))

d %<>% spread(key = number, value = value)

d %<>% 
  mutate(model = str_remove(model, "..[0-9].*")) %>% 
  rename(std.error = se) 

# Order models 
d$model <- factor(d$model, 
levels = unique(d$model), 
labels = unique(d$model))

shapes <- c(15,0,16,1,17,2)
names(shapes) <- levels(d$model)
colors <- viridis(length(levels(d$model)), option = "B", begin = 0, end = .8)
names(colors) <- names(shapes)
```


## Core models:
```{r guidance-exp-figure1, fig.height=2.5}
d %>% 
  filter(str_detect(model, " A|Model C| E")) %>% 
  guidplot(data) 

```

## Expanded models:
```{r guidance-exp-figure2, fig.height=7.5}
p <- d %>% 
  # filter(str_detect(model, " B| D| E")) %>% 
  guidplot(data)


b <- list(c("Org. Characteristics", "Health or Health Care" , "Size")
          )

p %>%
  add_brackets(b)

# p+ facet_grid(type ~., scales = "free_y", drop = TRUE) 
```

## Interaction 
In order to add errors to marginal effects, I need the covariance. 

It might be good to show the underlying data, which would look better (and be more accurate) for the 5pt scale, but could be jittered on 1 and 0.

```{r guidance-exp-interaction, fig.height=3, fig.width =4}
d %<>% 
  filter(str_detect(model, "Model A"))
#d %>% select(term, model, estimate, std.error)

d <- d$estimate
df <- tibble(group = c("Lobbied on Guidance", "Lobbied on Rule", "Lobbied on Rule", "Lobbied on Guidance"),
       condition = c("Guidance Vignette", "Rule Vignette", "Guidance Vignette", "Rule Vignette"),
       estimate = c(d[1]+ d[2] + d[3], 0, d[1], d[2] ) ) 
df

df %>% 
  ggplot(aes(y = estimate, 
             x= "", 
             color = condition, 
             label = condition)) + 
  facet_grid(. ~ group) +
  geom_label() + 
  scale_color_viridis_d(option = "B", begin = 0, end = .8) +
  labs(x = "", 
       y = "Anticipated influence",
       title = "Interaction (Model A)", 
       caption = "Estimates of Hypothetical Influence
1 = {\"somewhat,\" \"quite a bit,\" \"a great deal\"}
0 = {\"none at all\",\"little\"}")+
  theme(legend.position = "none",
        axis.ticks =  element_blank() )+
  scale_y_continuous(limits = c(-1,1))
```
The effect of the **guidance** condition for those that lobbied on **guidance** compared to: 

The **rule** condition for those that lobbied on **guidance**: `r df$estimate[1]-df$estimate[4]`

The **guidance** condition for those that lobbied on a **rule**: `r df$estimate[1]-df$estimate[3]`

The **rule** condition for those that lobbied on a **rule**: `r df$estimate[1]-df$estimate[2]`









# Experiment Results (5 point)
```{r guidance-exp5, fig.height=2.5}
data <- "Estimates of Hypothetical Influence
(Experimental Data)"
d <- readxl::read_excel(here("out/OutputA.xlsx"), 
                        range = "Sheet1!A1:C4") %>% 
  mutate(model = "Model A, General Influence",
         term = B_1A) %>% 
  full_join(readxl::read_excel(here("out/OutputC.xlsx"), 
                               range = "Sheet1!A1:C4") %>% 
              mutate(model = "Model C, Public Interest Group Influence",
                     term = B_1B) ) %>% 
  full_join(readxl::read_excel(here("out/OutputE.xlsx"), 
                               range = "Sheet1!A1:C4") %>%
              mutate(model = "Model E, Corporate Influence",
                     term = B_1C) ) 
  
d %<>% rename(estimate = Coef.,
              std.error = `Std. Err.`)

d$term %<>% str_replace("RAND_B1", "Experimental Condition") %>%
  str_replace("Rule_Guidance", "Guidance Document") %>% 
  str_replace("inter", "Interaction Effect")

# Order models 
d$model <- factor(d$model, 
levels = unique(d$model), 
labels = unique(d$model))

shapes <- c(15,0,16,1,17,2)
shapes <- c(15,16,17) # FIXME 
names(shapes) <- levels(d$model)
colors <- viridis(length(levels(d$model)), option = "B", begin = 0, end = .8)
names(colors) <- names(shapes)
```


## Core models:
```{r guidance-exp-figure15, fig.height=2.5}
d %>% 
  #filter(str_detect(model, " A|Model C| E")) %>% 
  guidplot(data) 
```

## Interaction
```{r guidance-exp-interaction5, fig.height=3, fig.width =4}
# d %>% select(term, model, estimate, std.error)

df <- tibble(group = c("Lobbied on Guidance", 
                       "Lobbied on Rule", 
                       "Lobbied on Rule", 
                       "Lobbied on Guidance"),
       condition = c("Guidance Vignette", 
                     "Rule Vignette", 
                     "Guidance Vignette", 
                     "Rule Vignette"),
       estimate = c(d$estimate[1]+ d$estimate[2] + d$estimate[3], 
                    0, 
                    d$estimate[1],
                    d$estimate[2] )#,
       #std.error = 
       ) 

df

df %>% 
  ggplot(aes(y = estimate, 
             x= "", 
             color = condition, 
             label = condition)) + 
  facet_grid(. ~group)+
  geom_label() + 
  scale_color_viridis_d(option = "B", begin = 0, end = .8) +
  labs(x = "", 
       y = "Anticipated influence",
       title = "Interaction (Model A)", 
       caption = "Estimates of Hypothetical Influence\n
5 = \"a great deal\",\n0 = \"none at all\"")+
  theme(legend.position = "none",
        axis.ticks =  element_blank())+
  scale_y_continuous(limits = c(-1,1))
```

The effect of the **guidance** condition for those that lobbied on **guidance** compared to: 

The **rule** condition for those that lobbied on **guidance**: `r df$estimate[1]-df$estimate[4]`

The **guidance** condition for those that lobbied on a **rule**: `r df$estimate[1]-df$estimate[3]`

The **rule** condition for those that lobbied on a **rule**: `r df$estimate[1]-df$estimate[2]`





For refrence:
For ğ‘Œ=ğ‘0+ğ‘1ğ‘‹+ğ‘2ğ‘+ğ‘3ğ‘‹ğ‘+ğ‘’
, the marginal effect is ğ‘1+ğ‘3â‹…ğ‘, a function of ğ‘. The variance of a weighted sum is ğ‘‰ğ‘ğ‘Ÿ(ğ‘1)+ğ‘‰ğ‘ğ‘Ÿ(ğ‘3)â‹…ğ‘2+2â‹…ğ‘â‹…ğ¶ğ‘œğ‘£(ğ‘1,ğ‘3), and the standard error is just the square root of that. You can get the covariance from the right off-diagonal element of the variance-covariance matrix of the coefficients. The variances will be found on the diagonal.

# Citations

@Anthony1992

@Baumgartner2009

@Baumgartner1993

@Baumgartner2001

@Bentham1843

@Browne1990

@Carpenter2002

@Carpenter2014a

@Coglianese2009

@Davis1971

@Dur2007

@Epstein1995

@FoodandDrugAdministration2011

@Franklin2010

@Funk2001

@Furlong1998

@Furlong2005

@Garrett2006

@Gluck2015

@Golden1998

@Graham2015

@Greve2014

@Haeder2015

@Hojnacki2012

@Hickman2009

@Hrebenar1996

@Hwang2014

@Kaufman1981

@Kaufman2001

@Kerwin2018

@Kingdon1995

@Kluver2013

@Levin2018

@Lewis2011

@Magill2004

@Mahoney2007JPP

@Manning1996

@Mantel2009

<!--@Mashaw1997-->

@McCubbins1987

@McCubbins1987

@Mendelson2007

@Naughton2009

@OfficeofManagementandBudget2007

@Parrillo2019

@Romano2014

@Romano2018

@Raso2010

@Rourke1984

@Rosenbloom2000

@Sabatier1988

@Schattschneider1975

@Seidenfeld2011

@Shapiro2014

@Stack2016

@Truman1951

@Warren2011

@West1995

@West2004

@Yackee2019

@Yackee2006JOP

@Young2017

# Bibliography